### 2010-12-03 report/report.tex
report

\editbox{mention using speed as evaluating factor, ``we started the
  robot, and it would collect data on its own.  if it walks otusdie fo
  the viewable area, it tells us and we move it back inside and
  restart it (but the data collection continues)''}

The metric for evaluation of the designed gait is speed. A comparison and evaluation. We stop each run after plateauing results (no improvement 
for one third of the policies seen so far)  (WHY??)

>>>>

\editbox{``we started the
  robot, and it would collect data on its own.  if it walks otusdie fo
  the viewable area, it tells us and we move it back inside and
  restart it (but the data collection continues)''}

The metric for evaluation of the designed gait is speed. We stop each 
run after plateauing results (no improvement for one third of the 
policies seen so far). The standard length of a run designates that it
should be stopped
